Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-04-27 Ben_Manuscripts/thesis/structure.tex
spell checking and mod to usage of subdiffusion

%  More highly selective nanoporous membranes would be extremely useful for
%  performing complex aqueous separations with seawater and various types of
%  wastewater. For example, Sodium chloride and boron in seawater
%  \cite{fritzmann_state---art_2007} and organic micropollutants found in
%  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
%  represent just a few of the diverse contaminants of water sources. By
%  efficiently separating contaminants from feed solutions with highly selective
%  membranes, it is possible to reduce the number of required membrane passes and
%  post-treatment steps needed for a given filtration process
%  \cite{werber_materials_2016}, thus lowering energy requirements. Additionally,
%  one can also extract valuable resources from the feed streams. For example,
%  flowback water produced during hydraulic fracturing of shale formations
%  contains dissolved species such as acetate whose extraction has economic value
%  \cite{dischinger_application_2017}.  
%
%  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
%  filtration processes that can be used to separate solutes on the order of 1 nm
%  in size and smaller, including ions. However, commercially available amorphous
%  RO membranes and porous NF membranes lack uniformity, which severely impacts
%  their selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their
%  fabrication involves the spontaneous assembly of polymers into disordered
%  structures that offer separation pathways that are tortuous and polydisperse in
%  size \cite{werber_materials_2016}. Tortuosity increases the effective length
%  that a solute must travel, while pore size polydispersity limits membrane
%  selectivity.
%
%  Ordered, nanostructured porous membrane materials have become an increasingly popular
%  research area for aqueous separation applications because they offer the
%  ability to control pore architecture at the molecular scale, thereby
%  permitting the design of solute-specific separation membranes
%  \cite{humplik_nanostructured_2011}. However, their development has been limited
%  by the ability to synthesize and scale various technologies. Graphene sheets
%  are atomically thick, which results in excellent water permeability but defects
%  during manufacturing severely impact selectivity
%  \cite{cohen-tanugi_multilayer_2016}.  Molecular dynamics (MD) simulations of
%  carbon nanotubes have shown promise \cite{humplik_nanostructured_2011}, but
%  synthetic techniques are unable to achieve scalable alignment and pore
%  monodispersity \cite{hata_water-assisted_2004,maruyama_growth_2005}.
%  Consequently, there is a need for new materials that could provide scalable
%  nanostructured porous membranes. 
%
%  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
%  (LLC) membranes can be produced at moderate scale and may be capable of
%  performing highly selective separations. LLCs are amphiphilic molecules that
%  have the ability to self-assemble into porous nanostructures
%  \cite{smith_ordered_1997} and can be cross-linked to create mechanically strong
%  membrane films with periodic pores on the order of 1 nm in diameter
%  \cite{zhou_supported_2005}. Unlike the pores in most commercial NF membranes,
%  polymeric LLC membrane pores are uniform in size because they are formed by
%  self-assembly. Since LLC polymer membranes lack an appreciable pore size
%  distribution, they inherently exhibit high selectivity due to their strict
%  molecular weight cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the
%  LLC monomers examined in this paper are salts, and therefore lead to Donnan
%  exclusion of ions in solution. The membrane gains a net surface charge when
%  counterions from the head groups that line the pore walls escape into the feed
%  solution in an effort to balance the gradients of concentration and electric
%  potential \cite{donnan_theory_1995}.    
%
%  The feasibility of nanostructured LLC polymer membranes for selective
%  separations has been demonstrated using LLC monomers that form the type 1
%  bicontinuous cubic (Q\textsubscript{I})
%  \cite{hatakeyama_water_2011,hatakeyama_nanoporous_2010,carter_glycerol-based_2012}
%  and the inverted hexagonal (H\textsubscript{II}) \cite{zhou_supported_2005}
%  phases. When separating organic solutes from NaCl, Q\textsubscript{I}-phase
%  membrane filtration experiments have shown selectivity 2--3 times higher than
%  commercial RO and 6--12 times higher than commercial NF membranes
%  \cite{dischinger_application_2017}. When separating a series of various sized
%  dyes, the H\textsubscript{II}-phase membrane showed complete rejection of dyes
%  bigger than 1.2 nm in size \cite{zhou_supported_2005}. 
%
%  The H\textsubscript{II}-phase pore geometry (Figure~\ref{fig:hex_packing_simple}) has a
%  higher theoretical capacity for transport than the Q\textsubscript{I} phase.
%  The H\textsubscript{II} phase forms at room temperature in the presence of
%  ca.~10 wt\% water and consists of hexagonally packed, hydrophilic pore
%  columns\cite{smith_ordered_1997}. In the absence of water, neat monomer will
%  form the same hexagonal columnar structure which, in the literature, has been
%  referred to as the Col\textsubscript{h} thermotropic
%  phase\cite{feng_scalable_2014}. Q\textsubscript{I}-phase membranes consist of
%  a tortuous network of three dimensionally interconnected pores that prevent
%  optimal through-plane transport. In contrast, the densely packed, non-tortuous
%  and uniform sized pores of H\textsubscript{II}-phase membranes represent the
%  ideal geometry for achieving high solute
%  flux\cite{matyka_tortuosity-porosity_2008}. However, the hexagonally packed LC
%  domains of the H\textsubscript{II}-phase generally form mutually unaligned
%  domains, which hurts membrane permeability. This domain scale misalignment had
%  inhibited further development of this technology, and research efforts were
%  focused on the Q\textsubscript{I} phase, whose geometry does not require
%  alignment~\cite{zhou_new_2007}. 
%
%  However, recently researchers have learned how to macroscopically align the
%  hexagonal domains which has revived research into H\textsubscript{II}-phase LLC
%  polymer membranes. In 2014, Feng et al.~showed that one can align Col\textsubscript{h}
%  domains, created by the ``dry" monomer Na-GA3C11, using a magnetic field
%  with subsequent cross-linking to lock the structure in
%  place\cite{feng_scalable_2014}. In 2016, Feng et al.~showed that one could
%  also obtain the same result by confining the neat monomer between PDMS or glass
%  substrates since hexagonal mesophases preferentially anchor perpendicular to
%  both surfaces\cite{feng_thin_2016}. Current experimental efforts are focused
%  on extending the method to the H\textsubscript{II} phase and characterizing
%  the performance of these newly aligned systems.
%
%  \begin{figure}
%	\centering
%	\begin{subfigure}{.3\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{NaGA3C11.pdf}
%		\caption{}~\label{fig:monomer}
%	\end{subfigure}
%	\begin{subfigure}{.3\textwidth}
%		\centering
%		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
%		\caption{}~\label{fig:atomistic_monomer}
%	\end{subfigure}
%	\begin{subfigure}{0.3\linewidth}
%		\centering
%		\includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
%		\caption{}~\label{fig:wedge}
%	\end{subfigure}
%		\begin{subfigure}{0.4\linewidth}
%		\centering
%		\includegraphics[width=0.6\textwidth]{columns.pdf}
%		\caption{}~\label{fig:wedge_layer}
%	\end{subfigure}
%	\begin{subfigure}{0.4\linewidth}
%		\centering
%		\includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
%		\caption{}~\label{fig:hex_packing_simple}
%	\end{subfigure}
%	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
%	exhibits wedge-like character. (d) Monomers stack on top of each other to
%	create columns with short range order, then assemble into pores with 
%	hydrophilic head groups (blue) facing towards the pore center. (e) The 
%	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
%  \end{figure}

@@

  We measured the intensity of R-spots by averaging the peak heights produced
  by radially integrating the patterns within the R-alkanes region
  (Figure~\ref{fig:rspots}). In some patterns, the spots are not easily
  discernable due to obstruction by other features. In that case, we report the
  average intensity at the intersection of R-alkanes with the $q_z$ value of
  R-double since that is where we expect it to appear based on experiment. Since
  R-double does not appear in our simulated patterns, we estimate where it should
  appear as half of the $q_z$ value of R-$\pi$.

@@

  \label{addition:rspots}
  Previous literature has attributed the R-spots reflection in this particular
  WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
  This explanation is not unfounded as there are examples in literature of
  systems where tilted liquid crystals give rise to reflections that resemble
  R-spots~\cite{percec_self-assembly_2009,gearba_homeotropic_2007}. We 
  measured the tilt angle of the alkane chains of the 280 K system by measuring
  the angle made by the vector extending from top to
  bottom of each tail with respect to the membrane plane. We found that it
  equilibrates to an average tilt angle of -2 $\pm$
  13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Even when we placed position restraints on the
  monomers in a tilted initial configuration, monomers quickly reduced their tilt
  relative to the $xy$ plane to an angle statisically indistinguishable from zero
  (see Section \ref{S-section:tail_tilt} of Appendix A).

@@

  Although exactly reproducing the experimental 2D-WAXS pattern required
  attention to minute structural details, we found that all systems showed
  similar radial distribution functions characterized by a gradual radial
  transition from a dense hydrophlic core to hydrophobic tails. This observation
  enables us to study new systems that have not been experimentally characterized
  with the expectation that any additional structural optimization will not
  greatly influence trends in transport property predictions. The compositional
  gradient itself raises questions about the nature of size-exclusion separations
  in systems without well-defined pore boundaries, which potentially could enable
  separations that vary with chemical identity as well as size.

>>>>

@@

  We measured the intensity of R-spots by averaging the peak heights produced
  by radially integrating the patterns within the R-alkanes region
  (Figure~\ref{fig:rspots}). In some patterns, the spots are not easily
  discernible due to obstruction by other features. In that case, we report the
  average intensity at the intersection of R-alkanes with the $q_z$ value of
  R-double since that is where we expect it to appear based on experiment. Since
  R-double does not appear in our simulated patterns, we estimate where it should
  appear as half of the $q_z$ value of R-$\pi$.

@@

  \label{addition:rspots}
  Previous literature has attributed the R-spots reflection in this particular
  WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
  This explanation is not unfounded as there are examples in literature of
  systems where tilted liquid crystals give rise to reflections that resemble
  R-spots~\cite{percec_self-assembly_2009,gearba_homeotropic_2007}. We 
  measured the tilt angle of the alkane chains of the 280 K system by measuring
  the angle made by the vector extending from top to
  bottom of each tail with respect to the membrane plane. We found that it
  equilibrates to an average tilt angle of -2 $\pm$
  13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Even when we placed position restraints on the
  monomers in a tilted initial configuration, monomers quickly reduced their tilt
  relative to the $xy$ plane to an angle statistically indistinguishable from zero
  (see Section \ref{S-section:tail_tilt} of Appendix A).

@@

  Although exactly reproducing the experimental 2D-WAXS pattern required
  attention to minute structural details, we found that all systems showed
  similar radial distribution functions characterized by a gradual radial
  transition from a dense hydrophilic core to hydrophobic tails. This observation
  enables us to study new systems that have not been experimentally characterized
  with the expectation that any additional structural optimization will not
  greatly influence trends in transport property predictions. The compositional
  gradient itself raises questions about the nature of size-exclusion separations
  in systems without well-defined pore boundaries, which potentially could enable
  separations that vary with chemical identity as well as size.

### 2020-04-27 Ben_Manuscripts/thesis/structure_si.tex
Updates to outline and minor changes to figures
spell checking and mod to usage of subdiffusion

\chapter{Test}

@@

  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{method:ionic_conductivity} & Calculate the 
  ionic conductivity using the Nernst-Einsten relationship and collective diffusion model. \\ \hline

@@

  Crosslinking of the the monomer Na-GA3C11 occurs via a UV initiated free
  radical polymerization (FRP) (Figure~\ref{S-fig:xlink_mech}). Head-to-tail addition
  takes place between terminal vinyl groups on each of the monomer tails. We
  only considered head-to-tail addition since it is the dominant propagation mode
  in the real system.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{Crosslink_mechanism.eps}
  \caption{Terminal vinyl groups present on each monomer tail react with free
	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
	  radicals react with the vinyl groups of other monomers in order to propagate
	  crosslinking.}\label{S-fig:xlink_mech}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{centroids.png}
		\caption{}\label{S-fig:centroids}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing.png}
        \caption{}\label{S-fig:tail_fronts}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing_middles.png}
        \caption{}\label{S-fig:tail_middles}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing_ends.png}
        \caption{}\label{S-fig:tail_ends}
        \end{subfigure}
        \caption{Monomer tails pack together hexagonally. (a) The center of mass
        of each tail-front (See Figure~\ref{S-fig:tail_sections}) is visualized as
        a blue sphere. The red sphere highlights an example of a tail-front 
        center of mass with its nearest neighbors (green spheres) surrounding it
        in a hexagonal pattern. (b) We calculated the angle between each tail-front
        center of mass and its nearest neighbor tail-front center of masses and 
        plotted the distribution. There are distinct peaks ca. $-60\degree$, $0\degree$ and
        $60\degree$ which is indicitive of hexagonal packing. (c) We repeated the 
        same procedure outlined in (a) and (b) with the tail-middles. There is still 
        a high degree of order. (d) We repeated the procedure again with the tail-ends.
        There is far less order at the ends of the tails where there is more
        space to fill.}\label{S-fig:tail_packing}
  \end{figure}

@@

  The appearance of R-double is likely a consequence of structure induced when
  vertically stacked monomer pairs share hydrogen bonds with a common water molecule (See
  Section~\ref{section:rdouble} of the main text). It is not a consequence of the 
  structure of water itself because R-double still persists if we removed water from 
  the trajectory which gives rise to the feature (Figure~\ref{S-fig:rdouble_water_removed}). 
  We quantified the occurence of pairing interactions by binning the $z$-positions of the center of mass of 
  the monomer head groups into 20 bins, the same number as the monomers per column. 
  This works relatively well since there is a high degree of correlation between
  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
  shares a water molecule with a head group vertically above it (See Figure~\ref{S-fig:pore_hbonds}).
  We calculated the discrete Fourier transform of the distributions in Figure~\ref{S-fig:pore_hbonds}
  which we used as a rough indicator of whether the head group arrangement will lead to R-double
  (Figure~\ref{S-fig:pore_hbonds_ft}). We see the strongest indicator of asymmetric monomer
  stacking in Pore 1 where the peaks at 0.76 \AA$^{-1}$ are clearly distinguishable, meaning
  there is periodicity at twice the $\pi$-stacking distance.

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{xlink_charts.pdf}
  \caption{There are minor differences between the physical properties of a
  crosslinked (xlink) system versus an uncrosslinked system. The sandwiched configuration (S)
  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
  configuration remains constant. The pore spacing of both systems decreases upon cross-linking.
  The vertical distance between stacked monomers increases in the sandwiched configuration
  and decreases in the parallel displaced configuration. The correlation length decreases
  in both configurations.}\label{S-fig:xlink}
  \end{figure}

>>>>

\chapter{Supporting Information to Chapter 2}

@@

  \texttt{/analysis/Ionic\_Conductivity.py} & \ref{method:ionic_conductivity} & Calculate the 
  ionic conductivity using the Nernst-Einstein relationship and collective diffusion model. \\ \hline

@@

  Cross-linking of the the monomer Na-GA3C11 occurs via a UV initiated free
  radical polymerization (FRP) (Figure~\ref{S-fig:xlink_mech}). Head-to-tail addition
  takes place between terminal vinyl groups on each of the monomer tails. We
  only considered head-to-tail addition since it is the dominant propagation mode
  in the real system.

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{Crosslink_mechanism.eps}
  \caption{Terminal vinyl groups present on each monomer tail react with free
	  radical initiators to create monomers with terminal vinyl radicals.  Vinyl
	  radicals react with the vinyl groups of other monomers in order to propagate
	  cross-linking.}\label{S-fig:xlink_mech}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{centroids.png}
		\caption{}\label{S-fig:centroids}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing.png}
        \caption{}\label{S-fig:tail_fronts}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing_middles.png}
        \caption{}\label{S-fig:tail_middles}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=\textwidth]{hexagonal_tail_packing_ends.png}
        \caption{}\label{S-fig:tail_ends}
        \end{subfigure}
        \caption{Monomer tails pack together hexagonally. (a) The center of mass
        of each tail-front (See Figure~\ref{S-fig:tail_sections}) is visualized as
        a blue sphere. The red sphere highlights an example of a tail-front 
        center of mass with its nearest neighbors (green spheres) surrounding it
        in a hexagonal pattern. (b) We calculated the angle between each tail-front
        center of mass and its nearest neighbor tail-front center of masses and 
        plotted the distribution. There are distinct peaks ca. $-60\degree$, $0\degree$ and
        $60\degree$ which is indicative of hexagonal packing. (c) We repeated the 
        same procedure outlined in (a) and (b) with the tail-middles. There is still 
        a high degree of order. (d) We repeated the procedure again with the tail-ends.
        There is far less order at the ends of the tails where there is more
        space to fill.}\label{S-fig:tail_packing}
  \end{figure}

@@

  The appearance of R-double is likely a consequence of structure induced when
  vertically stacked monomer pairs share hydrogen bonds with a common water molecule (See
  Section~\ref{section:rdouble} of the main text). It is not a consequence of the 
  structure of water itself because R-double still persists if we removed water from 
  the trajectory which gives rise to the feature (Figure~\ref{S-fig:rdouble_water_removed}). 
  We quantified the occurrence of pairing interactions by binning the $z$-positions of the center of mass of 
  the monomer head groups into 20 bins, the same number as the monomers per column. 
  This works relatively well since there is a high degree of correlation between
  columns in our system. Peaks in the distributions represent the scenario where a monomer head group
  shares a water molecule with a head group vertically above it (See Figure~\ref{S-fig:pore_hbonds}).
  We calculated the discrete Fourier transform of the distributions in Figure~\ref{S-fig:pore_hbonds}
  which we used as a rough indicator of whether the head group arrangement will lead to R-double
  (Figure~\ref{S-fig:pore_hbonds_ft}). We see the strongest indicator of asymmetric monomer
  stacking in Pore 1 where the peaks at 0.76 \AA$^{-1}$ are clearly distinguishable, meaning
  there is periodicity at twice the $\pi$-stacking distance.

@@

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=\textwidth]{xlink_charts.pdf}
  \caption{There are minor differences between the physical properties of a
  cross-linked (xlink) system versus an uncross-linked system. The sandwiched configuration (S)
  exhibits a smaller decrease in its ionic conductivity, while the parallel displaced (PD)
  configuration remains constant. The pore spacing of both systems decreases upon cross-linking.
  The vertical distance between stacked monomers increases in the sandwiched configuration
  and decreases in the parallel displaced configuration. The correlation length decreases
  in both configurations.}\label{S-fig:xlink}
  \end{figure}

### 2020-04-27 Ben_Manuscripts/thesis/transport.tex
spell checking and mod to usage of subdiffusion

%  Membranes capable of separating nm-sized solutes with high selectivity and
%  permeability are highly desirable for a number of applications. For example,
%  separation of salt from seawater or other briny sources can yield potable
%  drinking water.~\cite{fritzmann_state---art_2007} Removal of organic
%  micropollutants, such as personal care products, pesticides and
%  pharmaceuticals, from surface and groundwaters, can have large benefits for
%  public health.~\cite{schwarzenbach_challenge_2006} Finally, one can purify and
%  recover dissolved species present in complex hydraulic fracturing flowback
%  water waste streams which would help mitigate the effects of deep well
%  injection and can be sold for profit.~\cite{dischinger_application_2017} 
%
%  All of these separations are possible in part with current commercial
%  membrane separation techniques, but all still suffer from serious drawbacks.
%  Currently, reverse osmosis (RO) and nanofiltration (NF) dominate commercial
%  membrane separations of small molecules.~\cite{warsinger_review_2018} RO
%  membranes are typically dense polymer matrices that separate solutes based on
%  differences in their solubility and permeability in the membrane
%  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
%  selective separations, high feed pressures and thus large amounts of energy are
%  necessary in order to generate a useful permeate
%  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
%  nm-sized pores which can give the same permeate flux as RO with lower applied
%  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
%  size, limiting their selectivity.~\cite{werber_materials_2016}.
%
%  Under the right conditions, amphiphilic molecules can self-assemble into
%  ordered nanostructures that may be capable of performing highly selective
%  separations with permeabilities comparable to
%  NF.~\cite{alexandridis_amphiphilic_2000} The uniform-sized aqueous pores
%  characteristic of these types of systems enforce a molecular-size cut-off,
%  eliminating issues related to the polydisperity of NF
%  pores.~\cite{zhou_supported_2005} In addition to size-exclusion, it may be
%  possible to control the chemical environment within the nanopores by altering
%  the identities of the hydrophilic moieties that form the pores, affording
%  solute-specific separations.~\cite{dischinger_effect_2017}
%
%  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I
%  bicontinuous cubic (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
%  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010}
%  When cross-linked, these materials can function as mechanically strong
%  separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} phase
%  has hexagonally packed, straight pores which is the ideal geometry for high
%  throughtput separations. However, the synthesis of H\textsubscript{II}
%  membranes with highly aligned hexagonal mesophases has been a challenge that
%  has been met with limited success and has prevented the material's viability as
%  a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The
%  Q\textsubscript{I} phase consists of a three dimensional network of tortuous
%  and interconnected pores.  It's more facile synthesis has yielded it more
%  success. The latest Q\textsubscript{I} phase membranes have been shown to
%  exhibit selectivities higher than commercial NF and RO membranes with permeabilities
%  higher than commercial RO membranes.~\cite{dischinger_application_2017}
%
%  Although Q\textsubscript{I} membranes have shown promising results, it
%  is not clear how to controllably design them for specific separations
%  beyond what has already been achieved. Dischinger et al. found that they
%  do not separate purely on the basis of size. Empirical modeling revealed
%  correlations between various solute physicochemical properties and 
%  observed solute rejection. Although there was some agreement with their
%  empirical model, it does not offer a sufficiently detailed explanation
%  of governing molecular interactions.~\cite{dischinger_effect_2017}

@@

  In the remainder of the paper, we describe and quantify three trapping 
  mechanisms which give rise to subdiffusive solute transport behavior. 
  We describe the differences in solute motion, specifically their mean
  squared displacement (MSD), in conjunction with each solute's size and 
  chemical functionality. We show how distinct interactions with various
  monomer components as well as membrane water content hinders the motion 
  of solutes. We discuss how the interactions between specific solutes and
  the membrane depend on the solute's chemical functionality.

@@

  To determine the approximate ratio of water in the pores to tails, we
  equilibrated 4 systems where we initially placed water in the pores and in the
  tails in addition to a water reservoir between periodic images. We filled the
  pores of our initial configuraiton with water by running the GROMACS command
  \texttt{gmx solvate} on our initial configuration followed by the removal of
  any water molecules placed in the distal tail region. This method requires that
  we vary the monomer starting radius since the vacant space dictates the pore's
  water content. We then placed a defined number of water molecules into the
  distal tail region one at a time with a short energy minimization between each
  insertion. We chose to test systems with initial pore radii of 5, 6, 7 and 8
  \AA~with tail and pore water compositions given in
  Table~\ref{S-table:water_content}. We found that systems started with more
  water in the pores than tails tended to equilibrate relatively quickly with an
  approximate ratio of 3 water molecules in the pores to 2 in the tails.

@@

  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the ageing phenomenon.
  In systems such as ours where solutes show hopping behavior between long periods 
  of immobility, ageing is defined by the tendency of the average slope of an MSD 
  curve to decrease as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
  Since the maximum measured dwell time can be no longer than the total length of a simulated
  trajectory, longer dwell times are incorporated into the calculation as measurement
  time or trajectory length is increased, lowering the average MSD. Because the solute 
  MSDs are non-linear and because of the ageing phenomenon, we did not attempt to calculate
  a diffusion constant as one might for a Brownian particle with a linear MSD. Instead,
  the reported MSD values represent the average MSD for a given	solute after a 400
  ns time lag. Our results are shown to be insensitive to our choice of time lag in 
  Section~\ref{S-section:lag_sensitivity} of Appendix B.

@@

  We fit Equation~\ref{eqn:msd-stokes-einstein} so that it passed through the
  highest solute MSD. We assumed that the solute with the highest MSD exhibited
  the closest to Brownian behavior and therefore could set a rough boundary
  between subdiffusive, Brownian and superdiffusive MSDs. As a lower bound to our
  appoximation, we also plotted the uncorrected version of
  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the
  same value as the corrected curve for large radii.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and more frequent hops occur when solutes are close to the pore center.
  (b) The time-averaged MSD of ethanol is sublinear which suggests transport is
  governed by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

@@

  Our work demonstrates that there are important, atomistic features of nanostructed, 
  self-assembled materials that molecular simulation can play a key role in elucidating.
  The complex interplay between the inhomogeneous membrane structure, solute size and 
  solute functionality leads to a variety of solute-membrane interactions, many of which
  are quite subtle. For example, association between polar groups and ions is seldom 
  mentioned in the literature, but we could not give a complete mechanistic explanation
  of observed transport behavior without its consideration. We also observed that water
  and solutes partition into the tails, an area previously assumed to be devoid of solutes,
  which offers another route towards selectivity. The interactions we observed, along 
  with those that may arise in other self-assembled nanoporous membranes, have the 
  potential to produce an immense diversity of transport behavior, suggesting that a 
  previously unexplored range of chemical selectivities may be possible. Atomistic 
  molecular modeling is likely to be highly useful in uncovering important mechanisms
  that will inspire and accelerate novel design by experimentalists.

>>>>

@@

  In the remainder of the paper, we describe and quantify three trapping 
  mechanisms which give rise to subdiffusive solute transport behavior
  %BJCF: added
  on timescales of hundreds of nanoseconds. 
  We describe the differences in solute motion, specifically their mean
  squared displacement (MSD), in conjunction with each solute's size and 
  chemical functionality. We show how distinct interactions with various
  monomer components as well as membrane water content hinders the motion 
  of solutes. We discuss how the interactions between specific solutes and
  the membrane depend on the solute's chemical functionality.

@@

  To determine the approximate ratio of water in the pores to tails, we
  equilibrated 4 systems where we initially placed water in the pores and in the
  tails in addition to a water reservoir between periodic images. We filled the
  pores of our initial configuration with water by running the GROMACS command
  \texttt{gmx solvate} on our initial configuration followed by the removal of
  any water molecules placed in the distal tail region. This method requires that
  we vary the monomer starting radius since the vacant space dictates the pore's
  water content. We then placed a defined number of water molecules into the
  distal tail region one at a time with a short energy minimization between each
  insertion. We chose to test systems with initial pore radii of 5, 6, 7 and 8
  \AA~with tail and pore water compositions given in
  Table~\ref{S-table:water_content}. We found that systems started with more
  water in the pores than tails tended to equilibrate relatively quickly with an
  approximate ratio of 3 water molecules in the pores to 2 in the tails.

@@

  We fixed the length of each simulated trajectory so that we could compare the total
  MSD between different solutes without the influence of the aging phenomenon.
  In systems such as ours where solutes show hopping behavior between long periods 
  of immobility, aging is defined by the tendency of the average slope of an MSD 
  curve to decrease as the length of trajectories are increased~\cite{metzler_anomalous_2014}.
  Since the maximum measured dwell time can be no longer than the total length of a simulated
  trajectory, longer dwell times are incorporated into the calculation as measurement
  time or trajectory length is increased, lowering the average MSD. Because the solute 
  MSDs are non-linear and because of the aging phenomenon, we did not attempt to calculate
  a diffusion constant as one might for a Brownian particle with a linear MSD. Instead,
  the reported MSD values represent the average MSD for a given	solute after a 400
  ns time lag. Our results are shown to be insensitive to our choice of time lag in 
  Section~\ref{S-section:lag_sensitivity} of Appendix B.

@@

  We fit Equation~\ref{eqn:msd-stokes-einstein} so that it passed through the
  highest solute MSD. We assumed that the solute with the highest MSD exhibited
  the closest to Brownian behavior and therefore could set a rough boundary
  between subdiffusive, Brownian and superdiffusive MSDs. As a lower bound to our
  approximation, we also plotted the uncorrected version of
  Equation~\ref{eqn:stokes-einstein} ($f$=1), requiring it to converge to the
  same value as the corrected curve for large radii.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{
  On the timescales simulated in our study, %<-- BJCF: added
  all solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and more frequent hops occur when solutes are close to the pore center.
  (b) The time-averaged MSD of ethanol is sublinear which suggests transport is
  governed by an anomalous subdiffusion process
  %BJCF: added
  on the hundreds of nanoseconds timescales simulated in this study  
  .}\label{fig:qualitative_mechanisms}
  \end{figure}

@@

  Our work demonstrates that there are important, atomistic features of nanostructured, 
  self-assembled materials that molecular simulation can play a key role in elucidating.
  The complex interplay between the inhomogeneous membrane structure, solute size and 
  solute functionality leads to a variety of solute-membrane interactions, many of which
  are quite subtle. For example, association between polar groups and ions is seldom 
  mentioned in the literature, but we could not give a complete mechanistic explanation
  of observed transport behavior without its consideration. We also observed that water
  and solutes partition into the tails, an area previously assumed to be devoid of solutes,
  which offers another route towards selectivity. The interactions we observed, along 
  with those that may arise in other self-assembled nanoporous membranes, have the 
  potential to produce an immense diversity of transport behavior, suggesting that a 
  previously unexplored range of chemical selectivities may be possible. Atomistic 
  molecular modeling is likely to be highly useful in uncovering important mechanisms
  that will inspire and accelerate novel design by experimentalists.

### 2020-04-27 Ben_Manuscripts/thesis/transport_si.tex
Updates to outline and minor changes to figures
spell checking and mod to usage of subdiffusion

chapter{Supporting Information to Chapter 3}\label{SI:ch3}

@@

  We can draw the same conclusions from any of the plots in Figure~\ref{S-fig:hbond_sensitivity}:
  \begin{enumerate}
    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
    interactions.
    \item The number of multiple-hydrogen-bond interactions increases.
    \item On average, propylene glcyol participates in more hydrogen bond interactions than 
    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
  \end{enumerate}

>>>>

\chapter{Supporting Information to Chapter 3}\label{SI:ch3}

@@

  We can draw the same conclusions from any of the plots in Figure~\ref{S-fig:hbond_sensitivity}:
  \begin{enumerate}
    \item An increased number of hydroxyl groups results in an increased number of hydrogen bond
    interactions.
    \item The number of multiple-hydrogen-bond interactions increases.
    \item On average, propylene glycol participates in more hydrogen bond interactions than 
    ethylene glycol.  %BJC: might need to label the total hydrogen bonds (put number centered on top of bars)
  \end{enumerate}
